---
title: "Rmarkdown and Leaflet Assignment"
author: "Alan Luscombe"
always_allow_html: yes
---

## Introduction

This work is based on the examples provided in the course.
It shows the location of Jeff Leek's office and some random point called "Alan's Office"
This document was knitted into HTML at the date-time below. 
```{r time_chunk, echo=TRUE, comment=""}
date()
```

### Initialise

```{r init_lib}
library("leaflet")
```


## Where is Alan's Office?

The following code shows some randomization of the location that is to have the "Alan's Office" text. Click on the markers to find Alan's Office location.

```{r where_is_office, eval=TRUE, echo=TRUE}
set.seed(2016-04-25)

df <- data.frame(lat = -runif(5, min = 8.8030, max = 53.8170),
                 lng = runif(5, min = -51.0021, max = 151.0092))

row.idx <- sample(1:dim(df)[[1]], 1)

df[-row.idx,] %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(lat=df[row.idx,1], lng=df[row.idx,2], 
             popup="Alan's Office") %>%
  addMarkers(lat=33.8, lng=-76.5898801, 
             popup="Jeff Leek's Office") %>%
  addMarkers(popup = "Not here")
```


## Conclusion

That worked, but I would like to make the location change each time after the marker is clicked. That's too involved for now.

I tried to put the popup's into the dataframe too, but that didn't work.
That way the text could have popped up with "not here" or such.
